State and Input Dependent Disturbances in Min-Max Model Predictive Control

### 2016-01-28 draft.tex
Abstract modified.
what happened

[ticket: X]
Introduced ticketing system.
what happened

[ticket: X]

@@

\newcommand{\todo}[1]{\textcolor{blue}{#1}}
\newcommand{\highlight}[1]{\textcolor{red}{#1}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
A robust model predictive control problem formulated as a sequence of min-max quadratic programs for a linear discrete time system with polytopic constraints is proposed.
%
The system is considered to be subject to additive disturbances which are realisations of a piecewise affine, state and input dependent disturbance set.
%
The analytic and algorithmic framework to accommodate state and input dependent disturbances in the computation of appropriate state constraint sets is presented and an algorithm that yields the convex maximal robust positive invariant set is proven to terminate in a finite number of iterations.
%
The min-max sequence is solved using an active-set based approach where the set of active constraints is updated via a line-search.
%
Throughout the paper a numerical example levitating ball system is used to illustrate the concepts.
\end{abstract}

@@

We assume that $\mathcal V(x)$ is a piecewise affine parametrically convex 
%point-to-set map defined 
set defined as in~\eqref{eq:definition:PWA:polytopic:set:general}:
\begin{equation}\label{eq:definition:PWA:polytopic:set:cl}
\mathcal{V}(x) = \Bigl\{ v : a_i v \leq\max_{k} \{ b_{i,k} + c_{i,k} x\} \ \forall i \in\mathbb N_m\Bigr\} ,
\end{equation}
%
and that $\mathcal{X}$ is convex and polyhedral:
\begin{equation}\label{eq:definition:polytopic:X}
\mathcal{X}=\{x : \xi_i x \leq 1\ \forall i \in\mathcal{I}_{\mathcal{X}} \} 
\end{equation}
where $\boldsymbol{\xi}_{\mathcal{I}_{\mathcal{X}}}=\Xi$.
%
We further assume (without loss of generality) that $\mathcal V(x)$ is compact for all finite $x\in\mathcal X$,
and can therefore be represented as the 
convex hull of its vertices: 
\begin{equation}\label{eq:definition:PWA:polytopic:set:vertices}
\mathcal V(x) = \conv\{v_j(x), \, j\in\mathbb{N}_q\} 
=  \conv\{\Theta_j x + \theta_j,\, j\in\mathbb{N}_q\}.
\end{equation}
%
Here $v_j(x)$ is necessarily piecewise affine in $x$ for all $j\in\mathbb{N}_q$ since ${\mathcal{V}}(x)$ is piecewise affine in $x$.
%

\begin{rem}\label{rem:pPdiff:calculation}
For a convex polyhedron $S=\{x : h_i x \leq 1$ $\forall i \in\mathcal{I} \}$ the parametric Pontryagin difference $S \ominus \mathcal{V}(S)$ is given by
%
%The parametric Pontryagin difference $S \ominus \mathcal{V}(S)$, for a convex polyhedral set $S=\{x : h_i x \leq 1\ \forall i \in\mathcal{I} \}$, is given by
%
%and a para\-met\-rically convex polytopic set $\mathcal{V}(x)$, we have 
% \begin{align*}
% S \ominus \mathcal{V}(S) 
% &= \{x : h_i x + \max_{v\in \mathcal{V}(x)} h_i v \leq 1 
% \ \forall i \in\mathcal{I} \}\\
% &= \{x : h_i x + \max_{j} h_i v_j(x) \leq 1 
% \ \forall i \in\mathcal{I}\}\\
% &= \{x : h_i x + \zeta_i(x) \leq 1 
% \ \forall i \in\mathcal{I}\}, \ 
% \zeta_i(x) = \max_{j} h_i v_j(x)
% \end{align*}
\begin{align*}
S \ominus \mathcal{V}(S) 
&= \{x : h_i x + \max_{v\in \mathcal{V}(x)} h_i v \leq 1 
\ \forall i \in\mathcal{I} \}\\
&= \{x : h_i x + \underbrace{\max_{j} h_i v_j(x)}_{=\zeta_i(x)} \leq 1 
\ \forall i \in\mathcal{I}\} .
\end{align*}
Here $\zeta_i(x)$ is the solution of a mpLP and hence is a continuous piecewise affine function of $x$~\cite{Gal:1995}. It follows that $S\ominus\mathcal{V}(S)$ is a convex polyhedral set.
%
To compute $\zeta_i(x)$ for all $x\in\mathcal X$ is in general a challenging problem, and a simpler method of determining the supporting hyperplanes of $S\ominus\mathcal{V}(S)$ is to include all possible affine inequalities in the set description:
\[
S\ominus\mathcal{V}(S) = \{ x : h_ix + h_i v_j(x) \leq 1, \ \forall j\in\mathbb{N}_q\ \forall i\in \mathcal I\}
\] 
and to subsequently remove redundant inequalities by applying an inequality reduction algorithm. 
% \textcolor{red}{%
The resulting set can be expressed $S\ominus \mathcal{V}(S) = \{ x : h_i^\prime x \leq 1 \ \forall i \in \mathcal{I}^\prime \}$.%
% }%
\end{rem}
%

@@

%We next provide conditions under which Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations.
% whenever the MRPI set $\mathcal X^\infty$ is non-empty. 
%
We next show that Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations if:
%
(i) $\Psi$ is asymptotically stable, and 
%
(ii) $\Gamma$ exists such that $(\Psi,\Gamma)$ is an observable pair and $\Gamma x$ is finite whenever $x\in\mathcal{X}$.
%
%We next show that, under mild conditions, Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations.
%
%, so that the spectral radius, $\rho$, of $\Psi$ satisfies $\rho < 1$. We denote the pre-image of a set $S$ under the linear map $\Psi$ as $\Psi^{-1}S$; 
%
The finite determinability of the MRPI set
$\mathcal X^\infty$ implies that there exists a finite number, $M$, such 
that $\mathcal X^\infty = \mathcal X_M$, and hence  $\mathcal{X}^\infty$ is defined by a finite set of linear inequalities whenever $\mathcal X^\infty\neq \emptyset$.
%
%that $x\in\mathcal X_M$ implies $\Psi x + v \in\mathcal X_M$ for all $v\in\mathcal V(x)$, and hence $\mathcal X^\infty = \mathcal X_M$.
%
\begin{thm}\label{thm:finite:MRPI:set:state:dependable}
Let $\rho < 1$, where $\rho$ is the spectral radius of $\Psi$, and let $\mathcal{X}\subseteq\mathcal{P}$, $\mathcal{P}=\{x:\Gamma x\leq{\bf{1}}\wedge 
-\Gamma x\leq{\bf{1}}\}$, where $(\Psi,\Gamma)$ is an observable pair.
%
Then the MRPI set $\mathcal X^\infty$ for the system $x^+ = \Psi x + v$ subject to disturbances $v\in\mathcal{V}(x)$, where $\mathcal V(x)$ is a continuous point-to-set map, and constraints $x\in\mathcal{X}$, is either empty or else is a bounded polytopic set satisfying $\mathcal X^\infty =\mathcal X_M$ for finite $M$.
\end{thm}
%
%
\begin{proof}
From~\eqref{eq:Xk:iteration} and Proposition~\ref{prop:Dk:iteration} it is clear that $\mathcal X^\infty$ is empty if $\mathcal{R}_k =\emptyset$ for some $k\geq 0$.
%
For the remainder of the proof we assume that $\mathcal{R}^\infty \neq \emptyset$ exists such that $\mathcal{R}_k \supseteq \mathcal{R}^\infty$ for all $k$.
%
The proof has two main steps: 
%
(i) we prove boundedness of $\mathcal X_k$ for all $k\geq n$, where $n$ is the state dimension;
%
(ii) we show that $\mathcal D_k$ grows exponentially with $k$, so that, for any bounded set $\mathcal C$, finite $M$ exists such that $\mathcal D_{M+1}\supseteq \mathcal{C}$. The proof is concluded by setting 
$\mathcal C = \mathcal X_{M}$ and deducing that $\mathcal X^\infty = \mathcal X_M$. 
%

For the first step, notice that $(\Psi,\Gamma)$ is observable if and only if $\mathrm{rank}(\mathcal{O}) = n$ where $\mathcal{O}^T=\begin{bmatrix} \Gamma^T \ \cdots \ 
(\Gamma\Psi^{n-1})^T\end{bmatrix}$, and this implies that the set 
%
\begin{equation}\label{eq:def:Pn}
\mathcal{P}_{n} = \{x: 
\mathcal O x\leq{\bf{1}}\wedge-\mathcal O x\leq{\bf{1}}\} = \bigcap_{k\in \mathbb N_{[0,n-1]}} \Psi^{-k} \mathcal{P}
\end{equation}
%
is bounded. 
%
(Here $\Psi^{-1}\mathcal{P}$ denotes the pre-image of $\mathcal{P}$ under the linear map $\Psi$, and $\Psi$ is not assumed to be an invertible matrix.)
%
But from (\ref{eq:Xk:iteration})-(\ref{eq:Rk:iteration}) and Proposition~\ref{prop:Dk:iteration} we have $\mathcal{D}_k\subseteq \Psi^{-k}\mathcal{X} \subseteq \Psi^{-k}\mathcal{P}$ and hence $\mathcal X_k\subseteq \mathcal P_k$ for all $k$. Therefore $\mathcal X_{n}$ is bounded and $\mathcal{X}^\infty$ is also bounded since $\mathcal{X}_k\supseteq\mathcal{X}_{k+1}\supseteq\mathcal{X}^\infty$ for all $k$.

To see that $\mathcal{D}_k$ grows exponentially, let $r_1$ be the radius of the largest ball centred on the origin that is contained in $\mathcal{R}^\infty$ so that $\mathcal{R}^\infty \supseteq r_1\mathcal{E}$ (where 
for notational convenience we write $\mathcal E=B_1(0)$). Then Proposition~\ref{prop:Dk:iteration} implies $\mathcal{D}_k=\Psi^{-k}\mathcal{R}_k\supseteq\rho^{-k}r_1\mathcal{E}$.

@@

To complete the proof, let $r_2$ denote the radius of the smallest ball centred on the origin that contains $\mathcal X_n$.
%(noting that $\mathcal X_p$ is necessarily bounded for $p\geq n$). 
%
Then, for any $k\geq n+1$ such that 
$\rho^{-k} r_1 \geq r_2$, 
we can conclude that $D_k\supseteq \mathcal X_n$ and, since $\mathcal X_n \supseteq \mathcal X_{k-1}$, we also have $D_k\supseteq \mathcal X_{k-1}$ so that 
$\mathcal X_k = \mathcal{X}_{k-1} \cap D_l$.
%
Therefore $\mathcal X^\infty = \mathcal X_M$ where
\begin{equation}\label{eq:iteration:bound}
M = \max \left\{ n , \left\lceil \frac{\log(r_2/r_1)}{\log(1/\rho)}\right\rceil - 1 \right\},
\end{equation}
and it follows that $\mathcal{X}^\infty$ is a bounded polytopic set.
\end{proof}
%

@@

\begin{rem}
The constants $c_1$, $c_2$, $c_3$ appearing in~(\ref{eq:iteration:cbound}) can be computed as follows:
\[
c_1 = \max_x \|x\|^2 \ \ \text{subject to} \ \  \Xi x\leq {\bf 1} ,
\]
which requires the solution of a (nonconvex) quadratic program (QP);
\[
c_2 = \max_{j\in\mathbb{N}_p} \|x_j\|^2 ,
\]
where 
%$x_j$ for $j\in\mathbb{N}_p$ are the vertices of $\mathcal{P}_n$;
$\mathcal{P}_n  =\conv\{x_j,\, j\in\mathbb{N}_p\}$; 
and
\[
c_3 = \max_{j\in\mathbb{N}_q} \max_x \|\Theta_jx + \theta_j\|^2 \ \  \text{subject to} \ \ \Xi x \leq {\bf 1} ,
\]
which requires the solution of $q$ (nonconvex) QPs.
\end{rem}

>>>>

%% Ticketing System
\usepackage{etoolbox}
\usepackage{xparse}
\NewDocumentCommand{\openTickets}{ > {\SplitList {,} } m }{\ProcessList{#1}{\BoolInit}}
\newcommand{\BoolInit}[1]{\providetoggle{#1}\toggletrue{#1}}
\newcommand{\todo}[2]{%
  \providetoggle{#1}%
    \iftoggle{#1}{%
    {\color{red}#2}%
    }{#2}
}

%% Ticket list
\openTickets{Manuel:wlog,Manuel:convHull,Manuel:remConcavity,Manuel:thm14:ref,Manuel:invertability:assumption,Manuel:inclusion:step,Manuel:minus:one}

@@

% \newcommand{\todo}[1]{\textcolor{blue}{#1}}
\newcommand{\highlight}[1]{\textcolor{red}{#1}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
A robust model predictive control problem formulated as a sequence of min-max quadratic programs for a linear discrete time system with polytopic constraints is proposed.
%
The system is considered to be subject to additive disturbances which are realisations of a piecewise affine, state and input dependent disturbance set.
%
The analytic and algorithmic framework to accommodate state and input dependent disturbances in the computation of appropriate state constraint sets is presented and an algorithm that yields the convex maximal robust positive invariant set is proven to terminate in a finite number of iterations.
%
The min-max sequence is solved using an active-set based approach where the set of active constraints is updated via a line-search.
%
Throughout the paper a levitating ball system is used to illustrate the concepts numerically.
\end{abstract}

@@

We assume that $\mathcal V(x)$ is a piecewise affine parametrically convex 
%point-to-set map defined 
set defined as in~\eqref{eq:definition:PWA:polytopic:set:general}:
\begin{equation}\label{eq:definition:PWA:polytopic:set:cl}
\mathcal{V}(x) = \Bigl\{ v : a_i v \leq\max_{k} \{ b_{i,k} + c_{i,k} x\} \ \forall i \in\mathbb N_m\Bigr\} ,
\end{equation}
%
and that $\mathcal{X}$ is convex and polyhedral:
\begin{equation}\label{eq:definition:polytopic:X}
\mathcal{X}=\{x : \xi_i x \leq 1\ \forall i \in\mathcal{I}_{\mathcal{X}} \} 
\end{equation}
where $\boldsymbol{\xi}_{\mathcal{I}_{\mathcal{X}}}=\Xi$.
%
We further assume \todo{Manuel:wlog}{(without loss of generality)} that $\mathcal V(x)$ is compact for all finite $x\in\mathcal X$,
and can therefore be represented as the 
convex hull of its vertices: 
\begin{equation}\label{eq:definition:PWA:polytopic:set:vertices}
\mathcal V(x) = \conv\{v_j(x), \, j\in\mathbb{N}_q\} 
=  \conv\{\todo{Manuel:convHull}{\max_{k}}
\Theta_{j\todo{Manuel:convHull}{,k}} x + \theta_{j\todo{Manuel:convHull}{,k}},\, j\in\mathbb{N}_q\}.
\end{equation}
%
Here $v_j(x)$ is necessarily piecewise affine in $x$ for all $j\in\mathbb{N}_q$ since ${\mathcal{V}}(x)$ is piecewise affine in $x$.
%

\begin{rem}\label{rem:pPdiff:calculation}
For a convex polyhedron $S=\{x : h_i x \leq 1$ $\forall i \in\mathcal{I} \}$ the parametric Pontryagin difference $S \ominus \mathcal{V}(S)$ is given by
%
%The parametric Pontryagin difference $S \ominus \mathcal{V}(S)$, for a convex polyhedral set $S=\{x : h_i x \leq 1\ \forall i \in\mathcal{I} \}$, is given by
%
%and a para\-met\-rically convex polytopic set $\mathcal{V}(x)$, we have 
% \begin{align*}
% S \ominus \mathcal{V}(S) 
% &= \{x : h_i x + \max_{v\in \mathcal{V}(x)} h_i v \leq 1 
% \ \forall i \in\mathcal{I} \}\\
% &= \{x : h_i x + \max_{j} h_i v_j(x) \leq 1 
% \ \forall i \in\mathcal{I}\}\\
% &= \{x : h_i x + \zeta_i(x) \leq 1 
% \ \forall i \in\mathcal{I}\}, \ 
% \zeta_i(x) = \max_{j} h_i v_j(x)
% \end{align*}
\begin{align*}
S \ominus \mathcal{V}(S) 
&= \{x : h_i x + \max_{v\in \mathcal{V}(x)} h_i v \leq 1 
\ \forall i \in\mathcal{I} \}\\
&= \{x : h_i x + \underbrace{\max_{j} h_i v_j(x)}_{=\zeta_i(x)} \leq 1 
\ \forall i \in\mathcal{I}\} .
\end{align*}
Here $\zeta_i(x)$ is the solution of a mpLP and hence is a continuous \todo{Manuel:remConcavity}{and concave} piecewise affine function of $x$~\cite{Gal:1995}. It follows that $S\ominus\mathcal{V}(S)$ is a convex polyhedral set.
%
To compute $\zeta_i(x)$ for all $x\in\mathcal X$ is in general a challenging problem, and a simpler method of determining the supporting hyperplanes of $S\ominus\mathcal{V}(S)$ is to include all possible affine inequalities in the set description:
\[
S\ominus\mathcal{V}(S) = \{ x : h_ix + h_i v_j(x) \leq 1, \ \forall j\in\mathbb{N}_q\ \forall i\in \mathcal I\}
\] 
and to subsequently remove redundant inequalities by applying an inequality reduction algorithm. 
% \textcolor{red}{%
The resulting set can be expressed $S\ominus \mathcal{V}(S) = \{ x : h_i^\prime x \leq 1 \ \forall i \in \mathcal{I}^\prime \}$.%
% }%
\end{rem}
%

@@

%We next provide conditions under which Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations.
% whenever the MRPI set $\mathcal X^\infty$ is non-empty. 
%
We next show that Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations if:
%
(i) $\Psi$ is asymptotically stable, and 
%
(ii) $\Gamma$ exists such that $(\Psi,\Gamma)$ is an observable pair and $\Gamma x$ is finite whenever $x\in\mathcal{X}$.
%
%We next show that, under mild conditions, Algorithm~\ref{alg:MRPI:set} is guaranteed to terminate after a finite number of iterations.
%
%, so that the spectral radius, $\rho$, of $\Psi$ satisfies $\rho < 1$. We denote the pre-image of a set $S$ under the linear map $\Psi$ as $\Psi^{-1}S$; 
%
The finite determinability of the MRPI set
$\mathcal X^\infty$ implies that there exists a finite number, $M$, such 
that $\mathcal X^\infty = \mathcal X_M$, and hence  $\mathcal{X}^\infty$ is defined by a finite set of linear inequalities whenever $\mathcal X^\infty\neq \emptyset$.
%
%that $x\in\mathcal X_M$ implies $\Psi x + v \in\mathcal X_M$ for all $v\in\mathcal V(x)$, and hence $\mathcal X^\infty = \mathcal X_M$.
%
\begin{thm}\label{thm:finite:MRPI:set:state:dependable}
Let $\rho < 1$, where $\rho$ is the spectral radius of $\Psi$, and let $\mathcal{X}\subseteq\mathcal{P}$, $\mathcal{P}=\{x:\Gamma x\leq{\bf{1}}\wedge 
-\Gamma x\leq{\bf{1}}\}$, where $(\Psi,\Gamma)$ is an observable pair.
%
Then the MRPI set $\mathcal X^\infty$ for the system $x^+ = \Psi x + v$ subject to disturbances $v\in\mathcal{V}(x)$, where $\mathcal V(x)$ is a continuous \todo{Manuel:thm14:ref}{and piece-wise affine point-to-set map as defined in~\eqref{eq:definition:PWA:polytopic:set:cl}}, and constraints $x\in\mathcal{X}$, is either empty or else is a bounded polytopic set satisfying $\mathcal X^\infty =\mathcal X_M$ for finite $M$.
\end{thm}
%
%
\begin{proof}
From~\eqref{eq:Xk:iteration} and Proposition~\ref{prop:Dk:iteration} it is clear that $\mathcal X^\infty$ is empty if $\mathcal{R}_k =\emptyset$ for some $k\geq 0$.
%
For the remainder of the proof we assume that $\mathcal{R}^\infty \neq \emptyset$ exists such that $\mathcal{R}_k \supseteq \mathcal{R}^\infty$ for all $k$.
%
The proof has two main steps: 
%
(i) we prove boundedness of $\mathcal X_k$ for all $k\geq n$, where $n$ is the state dimension;
%
(ii) we show that $\mathcal D_k$ grows exponentially with $k$, so that, for any bounded set $\mathcal C$, finite $M$ exists such that $\mathcal D_{M+1}\supseteq \mathcal{C}$. The proof is concluded by setting 
$\mathcal C = \mathcal X_{M}$ and deducing that $\mathcal X^\infty = \mathcal X_M$. 
%

For the first step, notice that $(\Psi,\Gamma)$ is observable if and only if $\mathrm{rank}(\mathcal{O}) = n$ where $\mathcal{O}^T=\begin{bmatrix} \Gamma^T \ \cdots \ 
(\Gamma\Psi^{n-1})^T\end{bmatrix}$, and this implies that the set 
%
\begin{equation}\label{eq:def:Pn}
\mathcal{P}_{n} = \{x: 
\mathcal O x\leq{\bf{1}}\wedge-\mathcal O x\leq{\bf{1}}\} = \bigcap_{k\in \mathbb N_{[0,n-1]}} \Psi^{-k} \mathcal{P}
\end{equation}
%
is bounded. 
%
(Here $\Psi^{-1}\mathcal{P}$ denotes the pre-image of $\mathcal{P}$ under the linear map $\Psi$\todo{Manuel:invertability:assumption}{, and $\Psi$ is not assumed to be an invertible matrix}.)
%
But from (\ref{eq:Xk:iteration})-(\ref{eq:Rk:iteration}) and Proposition~\ref{prop:Dk:iteration} we have $\mathcal{D}_k\subseteq \Psi^{-k}\mathcal{X} \subseteq \Psi^{-k}\mathcal{P}$ and hence $\mathcal X_k\subseteq \mathcal P_k$ for all $k$. Therefore $\mathcal X_{n}$ is bounded and $\mathcal{X}^\infty$ is also bounded since $\mathcal{X}_k\supseteq\mathcal{X}_{k+1}\supseteq\mathcal{X}^\infty$ for all $k$.

To see that $\mathcal{D}_k$ grows exponentially, let $r_1$ be the radius of the largest ball centred on the origin that is contained in $\mathcal{R}^\infty$ so that $\mathcal{R}^\infty \supseteq r_1\mathcal{E}$ (where 
for notational convenience we write $\mathcal E=B_1(0)$). Then Proposition~\ref{prop:Dk:iteration} implies $\mathcal{D}_k=\Psi^{-k}\mathcal{R}_k\supseteq\todo{Manuel:inclusion:step}{\Psi^{-k}\mathcal R^\infty\supseteq}\rho^{-k}r_1\mathcal{E}$.

@@

To complete the proof, let $r_2$ denote the radius of the smallest ball centred on the origin that contains $\mathcal X_n$.
%(noting that $\mathcal X_p$ is necessarily bounded for $p\geq n$). 
%
Then, for any $k\geq n+1$ such that 
$\rho^{-k} r_1 \geq r_2$, 
we can conclude that $D_k\supseteq \mathcal X_n$ and, since $\mathcal X_n \supseteq \mathcal X_{k-1}$, we also have $D_k\supseteq \mathcal X_{k-1}$ so that 
$\mathcal X_k = \mathcal{X}_{k-1} \cap D_l$.
%
Therefore $\mathcal X^\infty = \mathcal X_M$ where
\begin{equation}\label{eq:iteration:bound}
M = \max \left\{ n , \left\lceil \frac{\log(r_2/r_1)}{\log(1/\rho)}\right\rceil \todo{Manuel:minus:one}{- 1} \right\},
\end{equation}
and it follows that $\mathcal{X}^\infty$ is a bounded polytopic set.
\end{proof}
%

@@

\begin{rem}
The constants $c_1$, $c_2$, $c_3$ appearing in~(\ref{eq:iteration:cbound}) can be computed as follows:
\[
c_1 = \max_x \|x\|^2 \ \ \text{subject to} \ \  \Xi x\leq {\bf 1} ,
\]
which requires the solution of a (nonconvex) quadratic program (QP);
\[
c_2 = \max_{j\in\mathbb{N}_p} \|x_j\|^2 ,
\]
where 
%$x_j$ for $j\in\mathbb{N}_p$ are the vertices of $\mathcal{P}_n$;
$\mathcal{P}_n  =\conv\{x_j,\, j\in\mathbb{N}_p\}$; 
and
\[
c_3 = \max_{j\in\mathbb{N}_q} \max_x \todo{Manuel:convHull}{\max_k} \|\Theta_{j\todo{Manuel:convHull}{,k}} x + \theta_{j\todo{Manuel:convHull}{,k}}\|^2 \ \  \text{subject to} \ \ \Xi x \leq {\bf 1} ,
\]
which requires the solution of $q$ (nonconvex) QPs.
\end{rem}
